Universal Anonymous Signatures

### 2022-06-07 prism-backend/research/gsac/security-gsac.tex
Updated sign-unforgeability proof.

\begin{theorem}[Anonymity of \GSACGen]
  \label{thm:anonymity-gsac}
  If the underlying $\NIZK^{\NIZKRel_{\Sign}}$ scheme is zero-knowledge and
  simulation-extractable, and the encryption system is IND-CCA secure,
  our \GSACGen construction satisfies anonymity as defined in
  \defref{def:anonymity-gsac}.
\end{theorem}

>>>>

\begin{theorem}[Issuance anonymity of \GSACGen]
  \label{thm:iss-anonymity-gsac}
  \todo{XXX}
\end{theorem}

\begin{theorem}[Signature anonymity of \GSACGen]
  \label{thm:sig-anonymity-gsac}
  If the underlying $\NIZK^{\NIZKRel_{\Sign}}$ scheme is zero-knowledge and
  simulation-extractable, and the encryption system is IND-CCA secure,
  our \GSACGen construction satisfies anonymity as defined in
  \defref{def:sig-anonymity-gsac}.
\end{theorem}
